Arrows for Parallel Computations

### 2017-12-07 paper/content/arrows.tex

Note that with the Kleisli type we can define an alternative to |(>>=)| with the signature |m a -> Kleisli m a b -> m b|. The difference between the definitions of Arrows and Monads becomes more clear when we compare this definition with the Arrow compose operator |(>>>)|: Monads are types that allow composition of computations, while Arrows \emph{are} computations.

>>>>

Note that with the Kleisli type we can define an alternative to |(>>=)| with the signature |m a -> Kleisli m a b -> m b|. The difference between the definitions of Arrows and Monads becomes more clear if we compare this with the signature of the Arrow compose operator |(>>>) :: arr a b -> arr b c -> arr a c|: Monads are types that allow composition of computations, while Arrows \emph{are} composable computations.

### 2017-12-07 paper/content/bestAndWorstBenchmarks.tex
minor

\begin{table}[]
\centering
\caption{Overhead in the benchmarks}
\label{tab:meanOverhead}
\captionsetup[subtable]{justification=centering}
\sisetup{
	table-number-alignment = center
}
\subfloat[\sudokutest 1000]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{S S[table-text-alignment = center] S[table-text-alignment = center]}
		vs.             & mean overhead & maximum normalized stdDev \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-1000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\label{sudokuMeanFactor-1000}
	\end{minipage}
}
\subfloat[\sudokutest 16000]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-16000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{sudokuMeanFactor-16000}
	\end{minipage}
}
\newline
\vspace*{0.5 cm}
\newline
\subfloat[\rmtest 11213 32]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-32.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\label{sm-rmMeanFactor-11213-32}
	\end{minipage}
}
\subfloat[\rmtest 11213 64]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-64.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{sm-rmMeanFactor-11213-64}
	\end{minipage}
}
\newline
\vspace*{0.5 cm}
\newline
\subfloat[\torustest (dist) 4096]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-torus/bestAndWorstTorus-4096.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\label{torusMeanFactor-4096}
	\end{minipage}
}
\subfloat[\rmtest (dist) 44497 256]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-rm/bestAndWorstRM-44497-256.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{dist-rmMeanFactor-44497}
	\end{minipage}
}
\newline
\vspace*{0.5 cm}
\newline
\subfloat[\jacobitest (dist) 3217]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-jacobi/bestAndWorstJacobi-3217.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{jacobiMeanFactor-3217}
	\end{minipage}
}
\subfloat[\jacobitest (dist) 4253]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-jacobi/bestAndWorstJacobi-4253.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{jacobiMeanFactor-4253}
	\end{minipage}
}
\end{table}

>>>>

\begin{table}[]
\centering
\caption{Overhead in the shared memory benchmarks}
\label{tab:meanOverheadSharedMemory}
\centering
\begingroup\catcode`"=9
\begin{tabular}{C{4cm} C{2cm} C{1.7cm} C{2.3cm} C{1.7cm}}
	\thead{Benchmark} & \thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} & \thead{runtime for \\ 16 cores} \\ \hline \\
	\multirow{3}{*}{\sudokutest 1000}
	\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-1000.csv}{}{& \vs & \meanOverhead & \maxStdDevForOverhead & \runtimeMaxCores \\}
	\\ \hline \\
	\multirow{3}{*}{\rmtest 11213 32}
	\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-32.csv}{}{& \vs & \meanOverhead & \maxStdDevForOverhead & \runtimeMaxCores \\}
	\\ \hline \\
	\multirow{3}{*}{\rmtest 11213 64}
	\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-64.csv}{}{& \vs & \meanOverhead & \maxStdDevForOverhead & \runtimeMaxCores \\}
\end{tabular}
\endgroup
\end{table}

\begin{table}[]
\centering
\caption{Overhead in the distributed memory benchmarks}
\label{tab:meanOverHeadDistributedMemory}
\centering
\begingroup\catcode`"=9
\begin{tabular}{C{4cm} C{2cm} C{1.7cm} C{2.3cm} C{1.7cm}}
	\thead{Benchmark} & \thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} & \thead{runtime for \\ 256 cores} \\ \hline \\
	\multirow{1}{*}{\torustest 4096}
	\csvreader[head to column names]{benchmarks/distributed-torus/bestAndWorstTorus-4096.csv}{}{& \vs & \meanOverhead & \maxStdDevForOverhead & \runtimeMaxCores \\}
	\\ \hline \\
	\multirow{1}{*}{\rmtest 44497 256}
	\csvreader[head to column names]{benchmarks/distributed-rm/bestAndWorstRM-44497-256.csv}{}{& \vs & \meanOverhead & \maxStdDevForOverhead & \runtimeMaxCores \\}
	\\ \hline \\
	\multirow{1}{*}{\jacobitest 3217}
	\csvreader[head to column names]{benchmarks/distributed-jacobi/bestAndWorstJacobi-3217.csv}{}{& \vs & \meanOverhead & \maxStdDevForOverhead & \runtimeMaxCores \\}
\end{tabular}
\endgroup
\end{table}
